Raising the Role of Vocabulary Hubs for Semantic Data Interoperability in Dataspaces

### 2024-06-12 EBDVF-2024/paper.qmd
Added to next steps

# Conclusion and Future Work
We presented an approach for dynamically binding datasets to semantic descriptions in a dataspace's Vocabulary Hub,
therefore facilitating data harmonization and easier data consumption.
We have implemented a first prototype of our approach, which builds on the integration of GraphDB and PoolParty.

The next steps include:
- Bringing it into an actual dataspace in practice, representing and integrating datasets from different dataspace participants.
- Implementing use cases for richer discoverability, harmonized querying and support for different content types of structured and unstructured data.
Also, the ML should actually benefit regarding quality in practice, which still needs to be verified.

>>>>

# Conclusion and Future Work
We presented an approach for dynamically binding datasets to semantic descriptions in a dataspace's Vocabulary Hub,
therefore facilitating data harmonization and easier data consumption.
We have implemented a first prototype of our approach, which builds on the integration of GraphDB and PoolParty.
As next steps, we will bring this solution into use cases and into broader discussion to gain insight and develop it further.

The next steps include:
- Bringing it into actual dataspaces in practice, representing and integrating datasets from different dataspace participants.
- Implementing use cases for richer discoverability, harmonized querying and support for different content types of structured and unstructured data.
- Explore how ML can benefit regarding quality in practice when providing consolidated and cleaned data via dataspaces.
- Discuss how we can extend the IDS-RAM with services to improve the support for semantic interoperability provided by our solution.
